\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-22 notes/2loopNLSM.tex
added in appropriate ek and kk scaling for polarization blocks

As can be seen above, the Jacobi identity of \cref{cubicJac} fails
only in terms with two factors of polarization dot products,
$(\varepsilon\varepsilon)^2$. If we restricted ourselves to
just considering factors with a single polarization dot product, the
Jacobi identity of Yang-Mills would be satisfied \textit{off-shell}
and in arbitrary spacetime dimensions
\begin{equation}
{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0\,.
\end{equation}
This restriction to the $(\varepsilon\varepsilon)^1$ cubic sector of Yang-Mills is closely related to the MHV decomposition of color-dual numerators \cite{TasiLance,ElvangHuangReview,Chen:2019ywi,Chen:2021chy}.
In the MHV sector it is possible to choose the reference vectors so that all dot products of polarization vectors vanish, $(\varepsilon\varepsilon) \rightarrow 0$, except those involving one of the positive helicity polarizations, $\varepsilon^+_1 \varepsilon^-_i \neq 0$.
We describe this in detail in \cref{Conventions}.
By focusing on $(\varepsilon\varepsilon)$ structure rather than specific 4D helicity states, we will be able to construct dimension agnostic color dual integrands at one-loop.

@@

\subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
As we argued above, if we include factors of
$(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to
keep the Yang-Mills four-point contact for color-kinematics duality to
be restored on-shell. However, the contrapositive is also true -- if
we omit the four-point Yang-Mills vertex, then we only need terms that
contribute to the manifestly color-dual cubic sector of the theory.

We can achieve this construction by splitting the gauge group of the
full Yang-Mills action from $G$ to $G_L \times G_R$, where the full
non-abelian gauge symmetry is restored only when we identify
$G_L = G_R$. However, if we break the left gauge group down to
$G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to
$G_R \rightarrow U(N)$, then we are left with a semi-abelian theory
that is gauge invariant in the preferred $U(1)$-directions. We call
this manifestly color-dual theory \textit{semi-abelian Yang-Mills},
\begin{eBox}
\begin{equation}
\label{eq:semiYM}
\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
\end{equation}
\end{eBox}
where
\begin{equation}
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
\end{equation}
\begin{equation}
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
\end{equation}
and $A_\mu$ is in Lorenz gauge.
Here we can think of the abelian vector as a background field that
sources on-shell $A_\mu$ currents. Indeed, as we describe in
\cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
heart of $YZ$-theory \cite{Cheung:2016prv}, $J$-theory
\cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
\cite{Monteiro2011pc}.  Specifically, semi-Abelian YM is simply a
clever reinterpretation of the Lagrangian obtained by integrating an
auxiliary field into the $J$-theory equations of motion.  The Feynman
rule for the cubic vertex is
\begin{equation}
  \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{equation}
where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply
\be
\propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}.
\ee
We can use the Ward identity of
\cref{eq:GIrelA} to check that the amplitudes are indeed gauge
invariant when the abelian polarizations are taken to be longitudinal,
$\bar{\varepsilon} \rightarrow k$.

As noted above, we can select out can manifestly cubic
sector of semi-abelian Yang-Mills from the full theory of \cref{eq:ym-lag} by selecting only $(\varepsilon^+\varepsilon^+)$ in light-cone gauge (i.e. SDYM) and one-minus at tree-level or by plugging in the on-shell states of $J$-theory \cite{Cheung:2020djz,Cheung:2021zvb} and
$YZ$-theory \cite{Cheung:2016prv}. Indeed, semi-YM is just the following blocks
in the expansion of Yang-Mills given in Ref.~\cite{Pavao:2022kog}
\begin{equation}
A(...,\bar{A}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
\end{equation}
and similarly so at one-loop
\begin{equation}
A(...)_{\text{1-loop}} = \Delta^{(\varnothing)}_{\text{1-loop}}\, .
\end{equation}
\jm{For the tree amplitude how about we use something like}
\begin{equation}
A(1,2...,i,...n)_{\text{tree}} = \sum_{i\neq j}\Delta^{(ij)}_{\text{tree}} \sim \sum (\varepsilon_i \varepsilon) (\varepsilon k)^{n-2} (kk)^{3-n}
\end{equation}
where $i$ is the $\bar{A}_\mu$ particle.
\jm{And something similar for 1-loop?  This is one of the more important results of the paper so I'd like to add some schematic version of the $\Delta$s to make this paragraph as self-contained and clear as possible even if it introduces some redundancy.}
To recover NLSM at one-loop, we need to extract the $D$-dependent part
that corresponds to an internal $\bar{Y}Y$-loop from extra-dimensional
scalars
\begin{eBox}
\begin{equation}
A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\varepsilon\rightarrow k}\, .
\end{equation}
\end{eBox}
Why must we take the derivative with respect to $D$? After all,
$J$-theory and $YZ$-theory both have well defined propagators for
internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we discuss
in \cref{sec:CKLagrangians}, all the $J$ and $Z$ states must be on-shell in order to
produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at
one-loop will not produce NLSM amplitudes. However, the internal
$YY$-loop is a valid forward limit for producing NLSM amplitudes,
since as constructed $YZ$-theory matches to NLSM for off-shell
Y-particles. We provide explicit expressions for these one-loop amplitudes in the next section.

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
\jm{Would it be alright to omit the coupling constants in this section?  I think we've done so elsewhere.}
Our first application of this theory for color-dual construction at
loop level is for self-dual Yang-Mills (SDYM). At tree-level, the
off-shell cubic vertices can be written in terms of light cone
coordinates \cite{Monteiro2011pc}:
\begin{equation}
X(p,k) = p_u k_w-p_w k_u
\end{equation}
At loop-level, this construction needs to be analytically continued to
general dimension in order to apply dimensional regularization at
one-loop. This can be done using the cubic semi-YM vertices of the
previous section:
\begin{equation} \label{DdimSDYM}
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{equation}
Plugging in on-shell all-plus helicity states in light-cone gauge will
yield precisely the 4D SDYM vertex, up to an unphysical phase:
  \begin{equation}
  \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}
 \end{equation}
where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge, and in the second step applied momentum conservation to redefinition of the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$ defined in \cref{Conventions}. Of course, the form of \cref{DdimSDYM} has the advantage of
permitting a $D$-dimensional construction of the one-loop
integrand. Below we provide a four-point example:
\begin{equation}
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle
\end{equation}
where $\ell_i = \ell-(k_1+k_2+\cdots+ k_i)$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+\ell_i)}\varepsilon^\nu_{(-\ell_i)}}=\eta^{\mu\nu}$ on all internal polarizations.
In general, the $n$-gon diagram would be,
\begin{equation}\label{SDYMnGon}
N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
\end{equation}
Due to the state-sum of internal loop factors,
$\sum {\varepsilon_{(+\ell)}\varepsilon_{(-\ell)}}\sim D$, the integrand above
depends explicitly on the spacetime dimension, $D$. By taking a
derivative\footnote{Another way to understand this derivative is that
  it selects the large $D$ behavior of the integrand.}, we can recover
the integrand needed for all-plus one-loop amplitudes with an internal
scalar:
\begin{equation}
\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)
\end{equation}
This integrand numerator with internal scalar loop is precisely what
one would obtain from the Feynman rules of $YZ$-theory, absent the $\bar{Z}Z$
internal vector loop. For more background, we refer the reader to
\cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator:
\begin{equation}\label{NLSMnGon}
N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
\end{equation}
Where we have define the antisymmetric kinematic variable,
$[ij] = \ell_i^2 - \ell_j^2$, since when plugging on longitudinal
modes, the $n$-gon can be re-expressed completely in terms of inverse
propagators, $2(k_i \cdot \ell_i) = \ell_{i}^2-\ell^2_{i-1}$. We have
verified through 10-point one-loop that this $n$-gon expression is a
valid color-dual representation for NLSM.

@@

In addition to the natural tree-level construction, we found that kinetic mixing
between the two gauge fields permits globally color-dual one-loop
integrands, and after plugging in suitable on-shell states, the integrands
produced by semi-abelian YM correspond are those of SDYM in \cref{SDYMnGon} 
and NLSM in \cref{NLSMnGon}.  Due to the
kinetic mixing that stems from the broken Bose symmetry, \cref{2loopTension} shows why it is
impossible to construct a two-loop integrand for semi-abelian YM theory. In \cref{2loopBoot}, we overcame this obstruction by successfully constructing two-loop NLSM numerators with an ansatz based bootstrap. However, we found that the same approach fails for two-loop pure Yang-Mills, and pin-pointed the failure point to a particular unitarity cut captured by \cref{chefsKiss}. Thus, obtaining a globally color-dual
integrand beyond one-loop then requires sacrificing more than just Bose
symmetry, and in this paper we have argued that off-shell locality must
be abandoned for color-dual constructions of multi-loop Yang-Mills. \footnote{An example of this can already be found in the literature, where Locality is relaxed in \cite{Mogull:2015adi} in
  order to obtain color-dual two-loop integrands with on-shell 4D states.} To expand the available function space, we propose that one should consider including rational functions of kinematics, rather than just polynomials.

>>>>

As can be seen above, the Jacobi identity of \cref{cubicJac} fails
only in terms with two factors of polarization dot products,
$(\varepsilon\varepsilon)^2$. If we restricted ourselves to
just considering factors with a single polarization dot product, the
Jacobi identity of Yang-Mills would be satisfied \textit{off-shell}
and in arbitrary spacetime dimensions
\begin{equation}
{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0\,.
\end{equation}
This restriction to the $(\varepsilon\varepsilon)^1$ cubic sector of Yang-Mills is closely related to the MHV decomposition of color-dual numerators \cite{TasiLance,ElvangHuangReview,Chen:2019ywi,Chen:2021chy}.
In the MHV sector it is possible to choose the reference vectors so that all dot products of polarization vectors vanish, $(\varepsilon\varepsilon) \rightarrow 0$, except those involving one of the positive helicity polarizations, $(\varepsilon^+_1 \varepsilon^-_i )\neq 0$.
We describe this in detail in \cref{Conventions}.
By focusing on $(\varepsilon\varepsilon)$ structure rather than specific 4D helicity states, we will be able to construct dimension agnostic color dual integrands at one-loop.

@@

\subsection{semi-abelian Yang-Mills theory}\label{semiYM}
As we argued above, if we include factors of
$(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to
keep the Yang-Mills four-point contact for color-kinematics duality to
be restored on-shell. However, the contrapositive is also true -- if
we omit the four-point Yang-Mills vertex, then we only need terms that
contribute to the manifestly color-dual cubic sector of the theory.

We can achieve this construction by splitting the gauge group of the
full Yang-Mills action from $G$ to $G_L \times G_R$, where the full
non-abelian gauge symmetry is restored only when we identify
$G_L = G_R$. However, if we break the left gauge group down to
$G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to
$G_R \rightarrow U(N)$, then we are left with a semi-abelian theory
that is gauge invariant in the preferred $U(1)$-directions. We call
this manifestly color-dual theory \textit{semi-abelian Yang-Mills},
\begin{eBox}
\begin{equation}
\label{eq:semiYM}
\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
\end{equation}
\end{eBox}
where
\begin{equation}
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
\end{equation}
\begin{equation}
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
\end{equation}
and $A_\mu$ is in Lorenz gauge.
Here we can think of the abelian vector as a background field that
sources on-shell $A_\mu$ currents. Indeed, as we describe in
\cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the
heart of $YZ$-theory \cite{Cheung:2016prv}, $J$-theory
\cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills
\cite{Monteiro2011pc}.  Specifically, semi-abelian YM is simply a
clever reinterpretation of the Lagrangian obtained by integrating an
auxiliary field into the $J$-theory equations of motion.  The Feynman
rule for the cubic vertex is
\begin{equation}
  \cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3)
  -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{equation}
where the incoming arrow is the abelianized gauge field, and the outgoing arrows the on-shell non-abelian vectors. The propagator is simply
\be
\propFrule{$A^\nu$}{$\bar{A}^\mu$}{$k \rightarrow $}{fermion2} = \frac{i}{k^2} \eta^{\mu\nu}.
\ee
We can use the Ward identity of
\cref{eq:GIrelA} to check that the amplitudes are indeed gauge
invariant when the abelian polarizations are taken to be longitudinal,
$\bar{\varepsilon} \rightarrow k$.

As noted above, we can select out can manifestly cubic
sector of semi-abelian Yang-Mills from the full theory of \cref{eq:ym-lag} by selecting only $(\varepsilon^+\varepsilon^+)$ in light-cone gauge (i.e. SDYM) and one-minus at tree-level or by plugging in the on-shell states of $J$-theory \cite{Cheung:2020djz,Cheung:2021zvb} and
$YZ$-theory \cite{Cheung:2016prv}. Indeed, semi-YM is just the following blocks
in the expansion of Yang-Mills given in Ref.~\cite{Pavao:2022kog}
\begin{equation}
A(A_1,...,\bar{A}_i,...,A_n)_{\text{tree}} = \sum_{i\neq j} (\varepsilon_i \varepsilon_j) \Delta^{(ij)}_{\text{tree}} \sim \sum_{i\neq j} (\varepsilon_i \varepsilon_j)  \sum_a \,[(\varepsilon k)^{n-2} (kk)^{3-n}]_a\,,
\end{equation}
and similarly so at one-loop
\begin{equation}
A(A_1,...,A_n)_{\text{1-loop}} = \Delta^{(\varnothing)}_{\text{1-loop}} \sim \sum_a\,[ (\varepsilon k)^{n} (kk)^{-n}]_a\, .
\end{equation}
where $[\,\cdots]_a$ are terms with appropriate powers of $(\varepsilon k)$ and $(kk)$. As we describe in detail in \cref{sec:CKLagrangians}, to recover NLSM at one-loop we need to extract the $D$-dependent part
that corresponds to an internal $\bar{Y}Y$-loop from extra-dimensional
scalars
\begin{eBox}
\begin{equation}
A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\varepsilon\rightarrow k}\, .
\end{equation}
\end{eBox}
Why must we take the derivative with respect to $D$? After all,
$J$-theory and $YZ$-theory both have well defined propagators for
internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we discuss
in \cref{sec:CKLagrangians}, all the $J$ and $Z$ states must be on-shell in order to
produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at
one-loop will not produce NLSM amplitudes. However, the internal
$YY$-loop is a valid forward limit for producing NLSM amplitudes,
since as constructed $YZ$-theory matches to NLSM for off-shell
Y-particles. We now provide explicit expressions for these one-loop amplitudes in the next section.

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
Our first application of this theory for color-dual construction at
loop level is for self-dual Yang-Mills (SDYM). As we have done throughout the text, we will set all coupling constants to unity. At tree-level, the
off-shell cubic vertices can be written in terms of light cone
coordinates \cite{Monteiro2011pc}:
\begin{equation}
X(p,k) = p_u k_w-p_w k_u
\end{equation}
At loop-level, this construction needs to be analytically continued to
general dimension in order to apply dimensional regularization at
one-loop. This can be done using the cubic semi-YM vertices of the
previous section:
\begin{equation} \label{DdimSDYM}
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{equation}
Plugging in on-shell all-plus helicity states in light-cone gauge will
yield precisely the 4D SDYM vertex, up to an unphysical phase:
  \begin{equation}
  \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}
 \end{equation}
where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge, and in the second step applied momentum conservation to redefinition of the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$ defined in \cref{Conventions}. Of course, the form of \cref{DdimSDYM} has the advantage of
permitting a $D$-dimensional construction of the one-loop
integrand. Below we provide a four-point example:
\begin{equation}
\simplebox = \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle
\end{equation}
where $\ell_i = \ell-(k_1+k_2+\cdots+ k_i)$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+\ell_i)}\varepsilon^\nu_{(-\ell_i)}}=\eta^{\mu\nu}$ on all internal polarizations.
In general, the $n$-gon diagram would be,
\begin{equation}\label{SDYMnGon}
N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
\end{equation}
Due to the state-sum of internal loop factors,
$\sum {\varepsilon_{(+\ell)}\varepsilon_{(-\ell)}}\sim D$, the integrand above
depends explicitly on the spacetime dimension, $D$. By taking a
derivative\footnote{Another way to understand this derivative is that
  it selects the large $D$ behavior of the integrand.}, we can recover
the integrand needed for all-plus one-loop amplitudes with an internal
scalar:
\begin{equation}
\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = 2^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)
\end{equation}
This integrand numerator with internal scalar loop is precisely what
one would obtain from the Feynman rules of $YZ$-theory, absent the $\bar{Z}Z$
internal vector loop. For more background, we refer the reader to
\cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator:
\begin{equation}\label{NLSMnGon}
N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =   [12][23]\cdots [n1]
\end{equation}
Where we have define the antisymmetric kinematic variable,
$[ij] = \ell_i^2 - \ell_j^2$, since when plugging on longitudinal
modes, the $n$-gon can be re-expressed completely in terms of inverse
propagators, $2(k_i \cdot \ell_i) = \ell_{i}^2-\ell^2_{i-1}$. We have
verified through 10-point one-loop that this $n$-gon expression is a
valid color-dual representation for NLSM.

@@

In addition to the natural tree-level construction, we found that kinetic mixing
between the two gauge fields permits globally color-dual one-loop
integrands, and after plugging in suitable on-shell states, the integrands
produced by semi-abelian YM correspond are those of SDYM in \cref{SDYMnGon} 
and NLSM in \cref{NLSMnGon}.  Due to the
kinetic mixing that stems from the broken Bose symmetry, \cref{2loopTension} shows why it is
impossible to construct a two-loop integrand for semi-abelian YM theory. In \cref{2loopBoot}, we overcame this obstruction by successfully constructing two-loop NLSM numerators with an ansatz based bootstrap. However, we found that the same approach fails for two-loop pure Yang-Mills, and pin-pointed the failure point to a particular unitarity cut captured by \cref{chefsKiss}. Thus, obtaining a globally color-dual
integrand beyond one-loop then requires sacrificing more than just Bose
symmetry, and in this paper we have argued that off-shell locality\footnote{An example of this can already be found in the literature, where locality is relaxed in \cite{Mogull:2015adi} in
  order to obtain color-dual two-loop integrands with on-shell 4D states.} must
be abandoned for color-dual constructions of multi-loop Yang-Mills. To expand the available function space, we propose that one should consider including rational functions of kinematics, rather than just polynomials.
